The pollination trade-off

### 2019-04-12 paper/cover-letter.Rnw
Add hugo's papers to Cover Letter

%-----------------------------------------------------------------------------%
% Letter class
\documentclass[a4paper, 11pt]{letter}
\usepackage{hyperref}
% Name of sender
\name{Fernando Cagua}
% Signature of sender
\signature{Fernando Cagua}
% Address of sender
\address
{
    Fernando Cagua\\
    \href{mailto:efc29@uclive.ac.nz}{efc29@uclive.ac.nz} \\
    University of Canterbury, \\
    New Zealand
}
\date{April 15, 2019}
%-----------------------------------------------------------------------------%
\begin{document}
% Name and address of receiver
\begin{letter}
{
    Prof. Tim Coulson,\\
    Editor-in-chief,\\
    Ecology Letters
}
% Opening statement
\opening{Dear Professor Coulson,}
% Letter body

@@

@@

At the time of submission, PDFs of any recent manuscripts or book chapters by the author or coauthors and cited in the present submission must be uploaded as supporting files. This includes all cited manuscripts by the author or coauthors published this year, last year, in press or submitted. These files are made accessible to referees with the understanding that "in press" and "submitted" manuscripts represent privileged communications which may not be cited or used in any way other than for reference while reviewing the current manuscript. If there is a particular reason why a file should not be made available to reviewers, please point this out and provide an explanation in the cover letter.

This manuscript has not been published, is not under consideration for publication elsewhere.
Thank you for your consideration.

>>>>

%-----------------------------------------------------------------------------%
% Letter class
\documentclass[a4paper, 11pt]{letter}
\usepackage{hyperref}
\usepackage[backend=bibtex,style=verbose,doi=false,isbn=false,url=false]{biblatex}
\addbibresource{phd-bibliography/pollen-competition.bib}
% Name of sender
\name{Fernando Cagua}
% Signature of sender
\signature{Fernando Cagua}
% Address of sender
\address
{
    Fernando Cagua\\
    \href{mailto:efc29@uclive.ac.nz}{efc29@uclive.ac.nz} \\
    University of Canterbury, \\
    New Zealand
}
\date{April 15, 2019}
%-----------------------------------------------------------------------------%
\begin{document}
% Name and address of receiver
\begin{letter}
{
    Prof. Tim Coulson,\\
    Editorial Office,\\
    Ecology Letters
}
% Opening statement
\opening{Dear Professor Coulson,}
% Letter body

@@

In this manuscript we show that

@@

Lastly, please note that the data used in this manuscript has been previously published\autocite{marrero_effect_2014,marrero_agricultural_2016,marrero_exotic_2017} by one of the co-authors, however the enclosed work represents a novel contribution for all involved and no related work published, in press, or submitted during this or last year has been cited.

Thank you for your consideration.
